---
title: "Analysis of Post Offices in the United States"
date: 2023-06-05
output: html_document
---


Importing the libraries
```{r setup, include=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

library(tidyverse)
library(tidytuesdayR)
library(scales)


```

Data Loading

```{r Load}

tt <- tt_load("2021-04-13")
tt$post_offices %>%
  add_count(name,orig_name, state,county1, sort=TRUE)%>%
  filter(n >= 2)%>%
  arrange(name, orig_name, state, county1)%>%View()

tt$post_offices %>%
  filter(county1 == "GRAND TRAVERSE", name == 'ACME')%>%View()

post_offices <- tt$post_offices %>%
  select(name, state, county1, established, discontinued, continuous,
         stamp_index, id,
         coordinates,
         latitude,
         longitude,
         gnis_dist,
         gnis_county,
         gnis_state
         )%>%
  filter(established >= 1750,
         is.na(discontinued) | discontinued >= established)

```

Selecting only necessary columns and replacing na values with the year 2003.
Particularly this is important for the post offices which were opened and discontinued in the same year.

```{r}
post_office_years = post_offices %>% select (name, state, established, discontinued, latitude, longitude)%>%
  replace_na(list(discontinued = 2003))%>%
  filter(discontinued <= 2020)%>%
  filter(!is.na(established))%>%
  mutate(year = map2(established, discontinued, seq))%>%
  unnest(year)
```

Plotting Years vs #Active post offices.
```{r}
post_office_years %>%
  count(year, name = 'n_post_offices')%>%
  ggplot(aes(year,n_post_offices))+
  geom_area()+
  labs(x = 'Years', y = '# of active post offices')

```

Getting cumulative post offices
```{r}
post_offices_cumulative = post_office_years%>%
  count(year,
        state = fct_lump(state, 16),
        name = 'n_post_offices') %>%
  mutate(state = fct_reorder(state, -n_post_offices, sum))

post_offices_cumulative%>%
  filter(state != 'Other')%>%
  ggplot(aes(year, n_post_offices, fill = state)) + 
  geom_area() +
  labs(x = "Year",
       y = '# of post offices currently active in the US')+
  facet_wrap(~state) + 
  theme(legend.position = "none")
           
         
```

Plotting closures
```{r}
post_office_closures = post_offices %>%
  filter(!is.na(discontinued))%>%
  filter(discontinued >=1750,
         established >=1750,
         discontinued <=2021)%>%
  count(state= fct_lump(state, 16),
        decade = 10 * (discontinued %/%10),
        name = 'n_closures') 


post_office_closures%>%
  mutate(state = fct_reorder(state, -n_closures, sum))%>%
  filter(state != 'Other')%>%
  ggplot(aes(decade, n_closures, fill = state)) + 
  geom_area() +
  labs(x = "Decade",
       y = '# of post offices closed in the given decade')+
  facet_wrap(~state) + 
  theme(legend.position = "none") + 
  labs(title='When and Where the most post offices closed?')

```

An isolated case study of post offices at the start of the decade in the states of PA and KY.
```{r}
post_office_closures%>%
  inner_join(post_offices_cumulative, by = c("state", "decade" = "year"))%>%
  mutate(pct_closed = n_closures / n_post_offices)%>%
  filter(n_post_offices >= 20) %>%
  filter(state %in% c("KY","PA"))%>%
  ggplot(aes(decade,pct_closed, color = state)) +
  geom_line() +
  scale_y_continuous(labels = percent)+
  labs(y = "% of offices open at the start of the decade that closed")
```
##Maps
```{r}
library(ggthemes)
post_office_years%>%
  filter(year == 2003)%>%
  count(state, sort = TRUE)

states_map <- map_data("state") %>%
  as_tibble() %>%
  mutate(state = state.abb[match(region, str_to_lower(state.name))]) %>%
  replace_na(list(state = "DC"))

post_office_years%>%
  filter(year == 2003)%>%
  count(state, sort = TRUE )%>%
  inner_join(states_map, by = 'state')%>%
  ggplot(aes(long, lat, group = group, fill = n))+
  geom_polygon()+
  theme_map()+
  labs(title = 'Map of the United States with the number of post offices in each state')
```


```{r}
library(ggthemes)

states_map <- map_data("state") %>%
  as_tibble() %>%
  mutate(state = state.abb[match(region, str_to_lower(state.name))]) %>%
  replace_na(list(state = "DC"))

library(historydata)

state_pops <- us_state_populations %>%
  mutate(state = state.abb[match(state, state.name)]) %>%
  replace_na(list(state = "DC"))

post_office_years %>%
  filter(year == 2003) %>%
  count(state, sort = TRUE) %>%
  inner_join(states_map, by = "state") %>%
  ggplot(aes(long, lat, group = group, fill = n)) +
  geom_polygon() +
  scale_fill_gradient2(low = "blue", high = "red",
                       midpoint = 750) +
  theme_map() +
  labs(fill = "# of post offices")

post_office_years %>%
  filter(year == 2000) %>%
  count(state, sort = TRUE) %>%
  inner_join(state_pops %>% filter(year == 2000), by = "state") %>%
  mutate(post_office_density = n / (population / 1e6)) %>%
  inner_join(states_map, by = "state") %>%
  ggplot(aes(long, lat, group = group, fill = post_office_density)) +
  geom_polygon() +
  scale_fill_gradient2(low = "blue", high = "red",
                       midpoint = 250) +
  theme_map() +
  labs(fill = "Post offices / M people")
```
```{r}
post_office_cumulative_all <- post_office_years %>%
  count(year,
        state,
        name = "n_post_offices")
by_state_year <- post_office_cumulative_all %>%
  left_join(state_pops, by = c("year", "state")) %>%
  mutate(post_office_density = n_post_offices / (population / 1e6))

by_state_year %>%
  filter(year %in% c(1800, 1850, 1900, 1950)) %>%
  inner_join(states_map, by = "state") %>%
  ggplot(aes(long, lat, group = group, fill = n_post_offices)) +
  geom_polygon() +
  scale_fill_gradient2(low = "blue", high = "red",
                       mid = "pink",
                       midpoint = 2000) +
  facet_wrap(~ year) +
  theme_map() +
  labs(fill = "Post offices")
   
```
```{r}
library(gganimate)
by_state_year %>%
  inner_join(states_map, by = "state") %>%
  ggplot(aes(long, lat, group = group, fill = n_post_offices)) +
  geom_polygon() +
  scale_fill_gradient2(low = "blue", high = "red",
                       mid = "pink",
                       midpoint = 2000) +
  transition_manual(year) +
  theme_map() +
  labs(fill = "Post offices",
       title = "{ current_frame }")
```
```{r}
post_office_years %>%
  filter(year == 2000)%>%
  ggplot(aes(longitude, latitude))+
  geom_point()

post_office_years %>%
  filter(year == 1900,
         !state %in% c("HI", "AK")) %>%
  ggplot(aes(longitude, latitude)) +
  borders("state") +
  geom_point(size = .01, alpha = .25) +
  theme_map() +
  coord_map()
anim <- post_office_years %>%
  filter(year %% 4 == 0) %>%
  filter(!state %in% c("HI", "AK")) %>%
  ggplot(aes(longitude, latitude)) +
  borders("state", colour = "lightgray") +
  geom_point(size = .01, alpha = .25, color = "#004B87") +
  transition_manual(year) +
  labs(title = "Post office locations in the continental US: { current_frame }") +
  theme_map() +
  coord_map()
animate(
  anim,
  nframes = 30,
  fps = 6,
  renderer = gifski_renderer()
)
anim_save("F:/PostOfficeAnalysis/post-office-dots-blue.gif")
```

